A New Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems

### 2023-01-30 notes/notes.tex
combined gen siam chapters into thesis
--no-message
cosmetic changes

\documentclass[12pt]{report}
% \documentclass{nature}
\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,pifont,enumitem}
% \usepackage[draft]{graphicx}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.7in,top=0.3in,bottom=1.4in]{geometry}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\newcommand{\cmark}{\ding{51}}%

\newcommand{\comment}[1]{{}}
\renewcommand{\arraystretch}{2}
\setlength\delimitershortfall{-2pt}
\setcounter{tocdepth}{1}
\pagestyle{headings}
\setlength{\headheight}{52pt}
\numberwithin{equation}{section}
\allowdisplaybreaks
\bibliographystyle{ieeetr}

@@

\chapter{Future goals}
\begin{enumerate}
\item The Mott metal-insulator transition:
	\begin{todolist}
	\item[\cmark] Obtain the metal insulator transition of the 2D Hubbard-Heisenberg model on the square lattice from the present formalism. 
	\item Determine the nature of the bath $\Sigma (k,\omega)$ in the metallic phase, insulating phase as well as at criticality.
	\item Investigate nature of the zero-temperature transition (order of transition, order parameter, etc)
	\end{todolist}

\item Higher-order Greens functions:
	\begin{todolist}
	\item Provide expressions for two-particle Greens functions.
	\item Calculate explicitly the Greens functions for holon-doublon and spinon-spinon excitations as they are likely to contain more information regarding the ground state.
	\item Obtain spectral functions for such excitations
	\end{todolist}

\item Benchmarking against ED and/or finite size scaling:
	\begin{todolist}
	\item ground state energy
	\item double occupancy
	\end{todolist}

\item Upgrade to two-site cluster:
	\begin{todolist}
	\item Study a two-impurity model under renormalisation group
	\item[\cmark] Derive the tiling and Greens function relations for such a two-impurity model 
	\item Demonstrate Mott MIT here.
	\item Investigate the nature of many-particle entanglement in such a cluster
	\item look for signs of a quantum liquid.
	\end{todolist}

>>>>

\documentclass{report}
\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,enumitem}
% \usepackage[draft]{graphicx}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.5in,bottom=1in]{geometry}

\newcommand{\comment}[1]{{}}
\setcounter{tocdepth}{1}
\numberwithin{equation}{section}
\allowdisplaybreaks
\bibliographystyle{unsrt}

@@

\chapter{Future goals}
\begin{enumerate}
\item The Mott metal-insulator transition:
	\begin{itemize}
	\item Obtain the metal insulator transition of the 2D Hubbard-Heisenberg model on the square lattice from the present formalism. 
	\item Determine the nature of the bath $\Sigma (k,\omega)$ in the metallic phase, insulating phase as well as at criticality.
	\item Investigate nature of the zero-temperature transition (order of transition, order parameter, etc)
	\end{itemize}

\item Higher-order Greens functions:
	\begin{itemize}
	\item Provide expressions for two-particle Greens functions.
	\item Calculate explicitly the Greens functions for holon-doublon and spinon-spinon excitations as they are likely to contain more information regarding the ground state.
	\item Obtain spectral functions for such excitations
	\end{itemize}

\item Benchmarking against ED and/or finite size scaling:
	\begin{itemize}
	\item ground state energy
	\item double occupancy
	\end{itemize}

\item Upgrade to two-site cluster:
	\begin{itemize}
	\item Study a two-impurity model under renormalisation group
	\item Derive the tiling and Greens function relations for such a two-impurity model 
	\item Demonstrate Mott MIT here.
	\item Investigate the nature of many-particle entanglement in such a cluster
	\item look for signs of a quantum liquid.
	\end{itemize}
